### 2023-10-31 generalExploration.Rmd
Working on fission (#4), draft with random split (not keeping kids in same communities, only partners)

    ## Fission
    overloaded=initcomus$size>Th
    if(sum(overloaded)>0){
        listcomu=sapply(population,"[[","community") ##keep list of agent in each commu to avoid that 
        for(split in which(overloaded)){
            print(paste("community",split,"with size",initcomus$size[split]))
            tosplit= (listcomu == split)
            #initcomus
            moving=sample(names(population)[tosplit],initcomus$size[split]/2)
        }

@@

sumcomu=sapply(popsum,"[[","community")
plot(1,1,ylim=range(0,sumcomu),xlim=c(0,ncol(sumcomu)),type="n")
lapply(1:K,function(k) lines(sumcomu[k,],col=mean(initcomus$adaptivetraits[k,])+1,lwd=2) )

>>>>

    ## Fission
    overloaded=initcomus$size>Th
    if(sum(overloaded)>0){
        listcomu=sapply(population,"[[","community") ##keep list of agent in each commu to avoid that 
        for(split in which(overloaded)){
            newcomunity=length(initcomus$size)+1
            print(paste("community",split,"with size",initcomus$size[split]))
            tosplit= (listcomu == split)
            #initcomus
            moving=sample(names(population)[tosplit],initcomus$size[split]/2)

            #resize communities
            initcomus$size[split]=initcomus$size[split]-length(moving)
            initcomus$size=c(initcomus$size,length(moving))

            #resize copy adaptive traits
            initcomus$adaptivetraits=rbind(initcomus$adaptivetraits,initcomus$adaptivetraits[split,])

            #position new community
            initcomus$adaptivetraits=rbind(initcomus$adaptivetraits,initcomus$adaptivetraits[split,])
            initcomus$coordinates=rbind(initcomus$coordinates,random2Dgrid(1,100))

            #move each agent and partner
            for( mov in moving){
                population[[mov]]$community = newcomunity
                part=population[[mov]]$partner 
                if(part>-1){
                    initcomus$size[population[[part]]$community]  =  initcomus$size[population[[part]]$community] - 1
                    population[[part]]$community = newcomunity
                    initcomus$size[newcomunity]=initcomus$size[newcomunity]+1
                }
            }
            print(paste("oldcoumnity",split,"is now",initcomus$size[split],"newcomunity",newcomunity,"of new size",initcomus$size[newcomunity]))
            #population[moving]=lapply(population[moving],function(m,nc){m$community=newcomunity;m})
            #could use that and then shoose randomly between parents
        }

@@

sumcomu=sapply(popsum,"[[","community")
plot(1,1,ylim=range(0,sumcomu),xlim=c(0,ncol(sumcomu)),type="n")
lapply(1:K,function(k) lines(sumcomu[[k]],col=mean(initcomus$adaptivetraits[k,])+1,lwd=2) )

moveA <- function(listmove,pop,newcom){
            for( m in listmove){
                pop[[m]]$community = newcom
            }
}

moveB <- function(listmove,pop,newcom){
    pop[moving]=lapply(pop[moving],function(m,nc){m$commnunity=nc;m},nc=newcom)
}

library(microbenchmark)
microbenchmark(moveA(moving,population,2),moveB(moving,population,2))
